---
title: "Step4_phenotype"
author: "Caylyn and Rose"
date: "7/26/2021"
output: html_document
---

###libraries
```{r}
install.packages("tidyr")
install.packages("dplyr")
install.packages("corrplot")
install.packages("reshape2")
install.packages("tidyverse")
install.packages("ggpubr")
install.packages("directlabels")
install.packages("ggplot2")
install.packages("plotly")
library(tidyr)
library(dplyr)
library(corrplot)
library(reshape2)
library(tidyverse)
library(ggpubr)
library(directlabels)
library(ggplot2)
library(plotly)Yes
```


### Allocating known genotype to each plant
```{r}

raspi_clean <- read.csv("~/Desktop/export.check.csv", header = T)
raspi_clean$raspi.ID <- as.character(raspi_clean$raspi.ID)
unique(raspi_clean$raspi.ID)

#Change genotype ID to each certain plant
Map <- read.csv("~/Desktop/Lab_Work/linc_RNA/phenotyping/Script/rose_script/control_exp_ml_geno_R2.csv", header = T)
Map$Raspi <- as.character(Map$Raspi)
Map$Geno <- as.character(Map$Geno)
Map$Camera <- as.character(Map$Camera)

raspi_clean$Cam.ID <- as.character(raspi_clean$Cam.ID)
raspi_clean$Geno = "genotype"



#replacing each genotype based on Slots
for (i in 1: nrow(Map)){
  if(nrow(raspi_clean[raspi_clean$raspi.ID == Map[i,1] & raspi_clean$Cam.ID == Map[i,2] & raspi_clean$ID == Map[i,4],]) == 0) next
  raspi_clean[raspi_clean$raspi.ID == Map[i,1] & raspi_clean$Cam.ID == Map[i,2] & raspi_clean$ID == Map[i,4],]$Geno = Map[i,5]
}

```

```{r}
#Re-oder dataframe based on Time and genotype
raspi_clean <- raspi_clean[
  order(raspi_clean[,14], raspi_clean[,6], raspi_clean[,15]),
]

#import select files to select plants of interests
select <- read.csv("~/Desktop/Lab_Work/linc_RNA/phenotyping/Script/rose_script/control_exp_select_R2.csv", header = T)

raspi_clean$select = "select"
select$Raspi <- as.character(select$Raspi)
select$camera <- as.character(select$camera)


for (i in 1:nrow(select)){
  if(nrow(raspi_clean[raspi_clean$raspi.ID == select[i,1] & raspi_clean$Cam.ID == select[i,2] & raspi_clean$ID == select[i,3],]) == 0) next
  raspi_clean[raspi_clean$raspi.ID == select[i,1] & raspi_clean$Cam.ID == select[i,2] & raspi_clean$ID == select[i,3],]$select = "TRUE"
}


raspi_select <- raspi_clean[raspi_clean$select == "TRUE",]
raspi_final <- raspi_select[raspi_select$Geno != "empty",]


raspi_final$ID <- as.character(raspi_final$ID)

```

### Plot Data based on rig
```{r}


rig_plot <- ggplot(data =,raspi_final , aes(x= all.min, y=area, color = ID)) 
rig_plot <- rig_plot + geom_line(alpha = 0.3,size = 0.6, aes(group= ID)) 
rig_plot <- rig_plot + facet_wrap(~ raspi.ID + Cam.ID, ncol=2) 
rig_plot <- rig_plot + xlab("Total Minutes After Start") 
rig_plot <- rig_plot +  ylab("Leaf area") 
rig_plot <- rig_plot + xlim(0,15000) + ylim(0,90000)


rig_plot


```

### Plot Data based on single rig (check) 
```{r}
raspiS_cameraA <- raspi_final[raspi_final$raspi.ID == "raspiS" & raspi_final$Cam.ID == "cameraA",]

Srig_plot <- ggplot(data = raspiS_cameraA, aes(x= all.min, y=area, color = ID)) 
Srig_plot <- Srig_plot + geom_line(alpha = 0.3,size = 0.8, aes(group= ID)) 
Srig_plot <- Srig_plot + facet_wrap(~ raspi.ID + Cam.ID, ncol=2) 
Srig_plot <- Srig_plot + xlab("Total Minutes After Start")
Srig_plot <- Srig_plot +  ylab("Leaf area") + xlim(0,15000) + ylim(0,90000)
Srig_plot

#write.csv(raspi_clean, "~/Desktop/Raspi_clean_file.csv")
```
### Convert plot into plotly
```{r}     
ggplotly(Srig_plot)
```


### Add a new index to represent each plant
```{r}
raspi_final$Index <- paste0(raspi_final$raspi.ID,"_",raspi_final$Cam.ID,"_",raspi_final$ID)
```

### Plot data based on genotype
```{r}

ggplot(data = raspi_final, aes(x= all.min, y=area, color = ID)) + 
  geom_line(alpha = 0.3,size = 0.8, aes(group= Index)) + facet_wrap(~ Geno, ncol=3) +
  geom_point(alpha = 0.6,size = 0.4, aes(group= Index)) + facet_wrap(~ Geno, ncol=3) +
  xlab("Total Minutes After Start") +  ylab("Leaf area") +
  stat_summary(fun=mean, size=1, geom="line", linetype = "dashed", color = 'red') +
  xlim(0,15000) + ylim(0,90000) +
  geom_dl(aes(label = Index), method = list(dl.trans(x = x - 1), "last.points", cex = 0.4))



```

### Calculate statistics and simplify dataframe
```{r}
#Calculate the mean, standard deviation for each genotype under certain condition per time stamp
raspi_final <- raspi_final
raspi_final <- raspi_final %>% group_by(all.min,Geno) %>% mutate(Genotype.Rep.number = n())
raspi_final <- raspi_final %>% group_by(all.min,Geno) %>% mutate(Genotype.area.mean = ave(area))
raspi_final <- raspi_final %>% group_by(all.min,Geno) %>% mutate(Genotype.area.std = sd(area))

raspi_final <- raspi_final[raspi_final$all.min < 3331 | raspi_final$all.min > 3479,]


#Simplify the stats dataframe 
Raspi_stats <- unique(raspi_final[,c(5,6,7,8,14,15,17,18,19,20)])

```

###calculating growth rate 
```{r}
#Build the Table for multiple linear regression to be written
Growth_rate_rep <- data.frame("Month" = integer(0), 
                             "Date" = integer(0),"Plant.ID" = character(0), "Genotype"= character(0), 
                             "intercept" = integer(0), "delta" = integer(0), "R.square" = integer(0))

#Build time schedule
sub_raspi_rep <- unique(Raspi_stats[,c(1,2,7,6)])
Growth_rate_rep$Plant.ID <- as.character(Growth_rate_rep$Plant.ID)
Growth_rate_rep$Genotype <- as.character(Growth_rate_rep$Genotype)


#Loop the calculation of linear fit of Day_time growth
for (x in 1:nrow(sub_raspi_rep)){
  #Name initial four columns
  Growth_rate_rep[x,1:4] <- sub_raspi_rep[x, 1:4]
  
  #Calculate the intercept
 Growth_rate_rep[x,5] <- lm(area ~ all.min, raspi_final[raspi_final$Month== as.integer(sub_raspi_rep[x,1]) & 
                                       raspi_final$Day == as.character(sub_raspi_rep[x,2]) & raspi_final$Geno == as.character(sub_raspi_rep[x,4]) &
                                       raspi_final$Index == as.character(sub_raspi_rep[x,3]),])$coefficient[[1]]
  
  #Calculate the delta
  Growth_rate_rep[x,6] <- as.numeric(lm(area ~ all.min, raspi_final[raspi_final$Month== as.integer(sub_raspi_rep[x,1]) & 
                                        raspi_final$Day == as.integer(sub_raspi_rep[x,2]) & raspi_final$Geno == as.character(sub_raspi_rep[x,4]) &
                                        raspi_final$Index == as.character(sub_raspi_rep[x,3]),])$coefficient[[2]])
  
  #Calculate the R.square
  Growth_rate_rep[x,7] <- summary(lm(area ~ all.min, raspi_final[raspi_final$Month== as.integer(sub_raspi_rep[x,1]) & 
                                        raspi_final$Day == as.integer(sub_raspi_rep[x,2]) & raspi_final$Geno == as.character(sub_raspi_rep[x,4]) &
                                        raspi_final$Index == as.character(sub_raspi_rep[x,3]),]))$r.squared
}
```

```{r}
#Clean and write final table
Growth_rate_rep <- na.omit(Growth_rate_rep)
head(Growth_rate_rep)


Growth_rate_rep <- Growth_rate_rep[Growth_rate_rep$Date > 4,]

for(i in 1:nrow(Growth_rate_rep)){
  Growth_rate_rep$Rig.ID[i] <- strsplit(Growth_rate_rep$Plant.ID[i], "_")[[1]][1]
}
```


```{r}
write.csv(Growth_rate_rep, "~/Desktop/Growth_rate_all_reps2.csv", row.names = FALSE)
```

### Pair-wise comparison between two genotypes and plot
```{r}

#raspi_clean <- read.csv("~/Desktop/Growth_rate_all_reps2.csv", header = T)



#Split into pair-wise comparison groups
comp_set1 <- Growth_rate_rep[Growth_rate_rep$Genotype == "Col-0" | Growth_rate_rep$Genotype == "SALK_131552",]
comp_set2 <- Growth_rate_rep[Growth_rate_rep$Genotype == "Col-0" | Growth_rate_rep$Genotype == "CS801986",]
comp_set3 <- Growth_rate_rep[Growth_rate_rep$Genotype == "Col-0" | Growth_rate_rep$Genotype == "CS814327",]
comp_set4 <- Growth_rate_rep[Growth_rate_rep$Genotype == "Col-0" | Growth_rate_rep$Genotype == "CS816382",]
comp_set5 <- Growth_rate_rep[Growth_rate_rep$Genotype == "Col-0" | Growth_rate_rep$Genotype == "CS817575",]
comp_set6 <- Growth_rate_rep[Growth_rate_rep$Genotype == "Col-0" | Growth_rate_rep$Genotype == "CS818434",]
comp_set7 <- Growth_rate_rep[Growth_rate_rep$Genotype == "Col-0" | Growth_rate_rep$Genotype == "CS825570",]
comp_set8 <- Growth_rate_rep[Growth_rate_rep$Genotype == "Col-0" | Growth_rate_rep$Genotype == "CS826207",]
comp_set9 <- Growth_rate_rep[Growth_rate_rep$Genotype == "Col-0" | Growth_rate_rep$Genotype == "CS826972",]
comp_set10 <- Growth_rate_rep[Growth_rate_rep$Genotype == "Col-0" | Growth_rate_rep$Genotype == "CS835523",]
comp_set11 <- Growth_rate_rep[Growth_rate_rep$Genotype == "Col-0" | Growth_rate_rep$Genotype == "CS835977",]
comp_set12 <- Growth_rate_rep[Growth_rate_rep$Genotype == "Col-0" | Growth_rate_rep$Genotype == "CS836960",]
comp_set13 <- Growth_rate_rep[Growth_rate_rep$Genotype == "Col-0" | Growth_rate_rep$Genotype == "CS837306",]
comp_set14 <- Growth_rate_rep[Growth_rate_rep$Genotype == "Col-0" | Growth_rate_rep$Genotype == "CS837491",]
comp_set15 <- Growth_rate_rep[Growth_rate_rep$Genotype == "Col-0" | Growth_rate_rep$Genotype == "CS840658",]
comp_set16 <- Growth_rate_rep[Growth_rate_rep$Genotype == "Col-0" | Growth_rate_rep$Genotype == "CS840668",]
comp_set17 <- Growth_rate_rep[Growth_rate_rep$Genotype == "Col-0" | Growth_rate_rep$Genotype == "SALK_080087",]



plot.df <- data.frame(set = c("comp_set1","comp_set2","comp_set3","comp_set4","comp_set5","comp_set6","comp_set7","comp_set8","comp_set9","comp_set10","comp_set11","comp_set12","comp_set13","comp_set14","comp_set15","comp_set16","comp_set17"),
                      graph = c("P1","P2","P3","P4","P5","P6","P7","P8","P9","P10","P11","P12","P13","P14","P15","P16","P17"))
  

#plot each pairwise-comparison of the growth rate

for (P in 1:nrow(plot.df)){
 plot_temp <- ggplot(data = get(plot.df[P,1]), aes(x = Date, y =delta, color = Genotype))+ 
   
    #plot each rep
   geom_line(alpha = 0.2, aes(group= Plant.ID)) + scale_colour_manual(values = c("dodgerblue3", "tomato1")) +
    #plot average lines
    stat_summary(fun=mean,  size=0.7, geom="line", linetype = "dashed") +
    #Add unit to the Y-axis
    ylab("Growth rate") + xlab("Days after experiment") +
    theme(legend.position = c(0.8,0.8)) +
    stat_compare_means(aes(x = Date), label = "p.signif", method = "t.test", hide.ns = T) + xlim(5,15) + ylim(0,20)
    
    #assign plot based on object name
   assign(plot.df[P,2],plot_temp)
}

P1
P2
P3
P4
P5
P6
P7
P8
P9
P10
P11
P12
P13
P14
P15
P16
P17

```
### Pairwise comparison of the growth rate from each two rig
Checking growth rate between rigs to find any significant differences that we may want to normalize to compare plants across rigs. 
```{r}
#Compare S to U
SU_list <- c("raspiU", "raspiS")
SU_subset <- subset(Growth_rate_rep, Growth_rate_rep$Rig.ID == SU_list)

SU_graph <-  ggplot(data = SU_subset, aes(x = Date, y =delta, color = Rig.ID))+ 
    #plot each rep
    geom_line(alpha = 0.2, aes(group= Plant.ID)) +
    #plot average lines
    stat_summary(fun=mean,  size=0.7, geom="line", linetype = "dashed") +
    #Add unit to the Y-axis
    ylab("Growth rate") + xlab("Days after experiment") +
    theme(legend.position = c(0.8,0.8)) +
    stat_compare_means(aes(x = Date), label = "p.signif", method = "t.test", hide.ns = T) +
   xlim(5,15) + ylim(0,10)
SU_graph

ST_list <- c("raspiS", "raspiT")
ST_subset <- subset(Growth_rate_rep, Growth_rate_rep$Rig.ID == ST_list)

ST_graph <-  ggplot(data = ST_subset, aes(x = Date, y =delta, color = Rig.ID))+ 
    #plot each rep
    geom_line(alpha = 0.2, aes(group= Plant.ID)) +
    #plot average lines
    stat_summary(fun=mean,  size=0.7, geom="line", linetype = "dashed") +
    #Add unit to the Y-axis
    ylab("Growth rate") + xlab("Days after experiment") +
    theme(legend.position = c(0.8,0.8)) +
    stat_compare_means(aes(x = Date), label = "p.signif", method = "t.test", hide.ns = T) +
   xlim(5,15) + ylim(0,10)
ST_graph

UT_list <- c("raspiU", "raspiT")
UT_subset <- subset(Growth_rate_rep, Growth_rate_rep$Rig.ID == UT_list)

UT_graph <-  ggplot(data = UT_subset, aes(x = Date, y =delta, color = Rig.ID))+ 
    #plot each rep
    geom_line(alpha = 0.2, aes(group= Plant.ID)) +
    #plot average lines
    stat_summary(fun=mean,  size=0.7, geom="line", linetype = "dashed") +
    #Add unit to the Y-axis
    ylab("Growth rate") + xlab("Days after experiment") +
    theme(legend.position = c(0.8,0.8)) +
    stat_compare_means(aes(x = Date), label = "p.signif", method = "t.test", hide.ns = T) +
   xlim(5,15) + ylim(0,10)
UT_graph
```
### Normalization of leaf area from each raspi rig



Found significant difference between rig N and P, so we are normalizing leaf area across rigs 
```{r}
#group based on each time point under each rig
#raspi_final <- raspi_final%>%group_by(raspi.ID)%>%mutate(Total_area = sum(area))

#calculate the ratio of area from each plant to total leaf area
#raspi_final$area_norm <- raspi_final$area/raspi_final$Total_area * 100000000 #relative ratio


#Build the Table for multiple linear regression to be written
#GR_norm <- data.frame("Month" = integer(0), 
                           #  "Date" = integer(0),"Plant.ID" = character(0), "Genotype"= character(0), 
                            # "intercept" = integer(0), "delta" = integer(0), "R.square" = integer(0))

#Build time schedule
#sub_raspi_rep <- unique(Raspi_stats[,c(1,2,7,6)])

#Loop the calculation of linear fit of Day_time growth
#for (x in 1:nrow(sub_raspi_rep)){
  #Name initial four columns
  #GR_norm[x,1:4] <- sub_raspi_rep[x, 1:4]
  
  #Calculate the intercept
  #GR_norm[x,5] <- lm(area_norm ~ all.min, raspi_final[raspi_final$Month== as.character(sub_raspi_rep[x,1]) & 
                                       # raspi_final$Day == as.character(sub_raspi_rep[x,2]) & #raspi_final$Geno == as.character(sub_raspi_rep[x,4]) &
                                       # raspi_final$Index == #as.character(sub_raspi_rep[x,3]),])$coefficient[[1]])
  
  #Calculate the delta
  #GR_norm[x,6] <- as.numeric(lm(area_norm ~ all.min, raspi_final[raspi_final$Month== as.character(sub_raspi_rep[x,1]) & 
                                        #raspi_final$Day == as.character(sub_raspi_rep[x,2]) & #raspi_final$Geno == as.character(sub_raspi_rep[x,4]) &
                                       # raspi_final$Index == #as.character(sub_raspi_rep[x,3]),])$coefficient[[2]])
  
  #Calculate the R.square
 # GR_norm[x,7] <- summary(lm(area_norm ~ all.min, raspi_select[Raspi_final$Month== as.character(sub_raspi_rep[x,1]) & 
                                        #raspi_final$Day == as.character(sub_raspi_rep[x,2]) & #raspi_final$Geno == as.character(sub_raspi_rep[x,4]) &
                                        #raspi_final$Index == as.character(sub_raspi_rep[x,3]),]))$r.squared
}

#GR_norm  <- GR_norm %>% separate(Plant.ID, c("RasPi.ID","Cam.ID","Plant.ID"))
#GR_norm$index <- paste0(GR_norm$RasPi.ID,"_",GR_norm$Cam.ID,"_",GR_norm$Plant.ID)


```

